The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-03-16 SI.tex
wait for next second

\begin{codefragment}{Python}
import time
import yaqc
temp = yaqc.Client(port=38003)
sensor = yaqc.Client(port=38004)
data = []
# begin heating
temp.set_position(100)
# take data until temp greater than 90 deg
while temp.get_position <= 90:
    sensor.measure()
    while sensor.busy():
        time.sleep(0.001)
    reading = dict()
    reading["timestamp"] = time.time()
    reading["temperature"] = temp.get_position()
    reading.update(sensor.get_measured())
    data.append(reading)
\end{codefragment}

>>>>

\begin{codefragment}{Python}
import time
import yaqc
temp = yaqc.Client(port=38003)
sensor = yaqc.Client(port=38004)
data = []
# begin heating
temp.set_position(100)
# take data until temp greater than 90 deg
while temp.get_position() <= 90:
    sensor.measure()
    while sensor.busy():
        time.sleep(0.001)
    reading = dict()
    reading["timestamp"] = time.time()
    reading["temperature"] = temp.get_position()
    reading.update(sensor.get_measured())
    data.append(reading)
    # wait for next second
    while time.time() - reading["timestamp"] < 1:
        time.sleep(0.001)
# stop heating
temp.set_position(25)
\end{codefragment}
